Individual Stellar Halos of Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-07-02 draft/paper1_v13.tex
New draft edited by Kevin

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG
% Version 7; MNRAS format; Edited by SH
% Version 10; MNRAS format; Edited by AL and JG
% Version 11; MNRAS format; Edited by SH
% Version 12; MNRAS format; Edited by SH

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halos of 
	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}

@@

    Massive galaxies display extended light profiles that can reach out to several 
    hundreds of kilo parsecs. 
    These stellar halos are a key fossil record of galaxy assembly history. 
    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    $i$-band), we present a systematic study of the stellar halos of a sample of more 
    than $7000$ galaxies at $0.3 < z < 0.5$. 
    Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which reaches ${\sim}4$ magnitudes 
    fainter than SDSS and enables us to directly trace mass profiles to 100 kpc 
    without resorting to stacking. 
    Shallow images and/or over-simplified parametric models cannot capture the extended 
    stellar halo and result in underestimated stellar masses.
    Our extended profiles reveal a number of mass-dependent trends. 
    The outer parts of our galaxies have higher ellipticity, and this ellipticity increases 
    with stellar mass, but we find no difference in color gradients with mass. 
    As in previous work, we see a clear trend towards more extended outer profiles 
    in more massive galaxies. 
    Thus, when this extended light is not properly accounted for, the stellar mass 
    function is systematically underestimated at the highest masses.
    Our results are broadly consistent with the two phase formation scenario of massive 
    galaxies in which outer envelopes are built up at late times from series of merging
    events. 
    We provide surface mass surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.

>>>>

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG
% Version 7; MNRAS format; Edited by SH
% Version 10; MNRAS format; Edited by AL and JG
% Version 11; MNRAS format; Edited by SH
% Version 12; MNRAS format; Edited by SH
% Version 13; MNRAS format; Edited by KB

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Mass Dependent Stellar Halos in Massive Galaxies]{Individual Stellar Halos of 
	   Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}
% \title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halos of 
% 	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}

@@

    Massive galaxies display extended light profiles that can reach several 
    hundreds of kilo parsecs. 
    These stellar halos provide a fossil record of galaxy assembly histories. 
    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    $i$-band), we present a systematic study of the stellar halos of a sample of more 
    than $7000$ galaxies at $0.3 < z < 0.5$ with $log M_{\star}/M_{\odot} > 11.4$. 
    Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which enables us to individually 
    estimate surface mass density profiles to 100 kpc without stacking. 
    As in previous work, we find that more massive galaxies exhibit more extended outer 
    profiles.  
    When this extended light is not properly accounted for as a result of shallow imaging 
    or inadequate profile modeling, the derived stellar mass function can be 
    significantly underestimated at the highest masses.  
    Across our sample, the ellipticity of outer light profiles increases substantially 
    as we probe larger radii.  
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at late times from a series of merging events. 
    We provide surface mass surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.
